\Title

### 2016-02-21 manuscript/manuscript.tex
Better note to reviewers regarding archived repo

All source code, data, and Jupyter notebooks
used here can be found at the online repository
\url{https://github.com/pinga-lab/paper-moho-inversion-tesseroids}.
An archived version is also available at
\url{http://dx.doi.org/DOI} (made available upon publication).
The repository also contains instructions for installing the necessary software
and reproducing all results presented here.

>>>>

All source code, data, and Jupyter notebooks
can be found at the online repository
\url{https://github.com/pinga-lab/paper-moho-inversion-tesseroids}.
The repository also contains instructions for replicating all results presented
here.
An archived version of this repository is also available at
\url{http://dx.doi.org/...}
(\textbf{Note to reviewers: the archived version will be uploaded only upon
publication}).
